---
title: "BMI Distribution from Health Survey England 1991"
output: html_notebook
---


# Read and clean data

Remove respondents with BMI >=50: from a technical point of view they make fitting the distribution difficult, from a strategic point of view, these individuals are at the top end of the morbidly obese group and are not in scope/unlikely to be impacted in any significant way by food environment interventions 

```{r}
library(tidyverse)
library(hrbrthemes)
library(fitdistrplus)
library(fitur)
library(actuar)

df <- read.table("C:\\Users\\Elena.Mariani\\Documents\\Projects\\ahl_weight_loss_modelling\\Data\\UKDA-7025-tab\\tab\\1991_2009hse.tab", sep = "\t", header = T)

df_1991 <- df %>% filter(year == "1992") # select year 1991 (survey collected in 1991)
nrow(df_1991)

df_valid <- df_1991 %>% filter(!is.na(bmivalid)) # remove respondents whose BMI value is not valid
nrow(df_valid)

df_low <- df_valid %>% filter(bmivalid < 45 & bmivalid > 15) # remove respondents with BMI higher than 50 and below 15
nrow(df_low)
```

# Describe Sample
```{r}
df_low %>% 
  group_by(sex) %>% 
  summarise(count = n())

df_low %>% 
  mutate(age_gr = cut(age, c(0,16,20,30,40,50,60,70,200), right = F, include.lowest = F)) %>% 
  group_by(age_gr) %>% 
  summarise(count = n())
```

# Fit Distributions by Male and Female Separately

## Males

```{r}
bmi90m <- df_low[which(df_low$sex == 1),"bmivalid"] %>% na.omit() %>% as.numeric()

## Step (1) Plot 
descdist( data = bmi90m , discrete = FALSE)
descdist(data = bmi90m, discrete = FALSE, boot=1000)


## Step (2) Fit

normal_ = fitdist(bmi90m, "norm")
weibull_ = fitdist(bmi90m, "weibull")
gamma_ = fitdist(bmi90m, "gamma")
invweibull_ = fitdist(bmi90m, "invweibull")
invgamma_ = fitdist(bmi90m, "invgamma")


plot(normal_)
plot(weibull_)
plot(gamma_)
plot(invweibull_)
plot(invgamma_)

## Step (3) Estimate parameters

print(normal_)
print(weibull_)
print(gamma_)
print(invweibull_)

summary(normal_)
summary(weibull_)
summary(gamma_)
summary(invweibull_)
summary(invgamma_)

gofstat(list(normal_, weibull_, gamma_, invweibull_, invgamma_), 
        fitnames=c("normal", "Weibull", "gamma", "inverseWeibull", "inverseGamma"))

# the best fitting distribution is the inverse gamma with parameters
# shape: 46.2399
# scale: 1161.3295
```
The best fitting distribution is the Inverse Gamma with parameters:

* shape = 46.3
* scale = 1161.3

### Simulate Distribution with Same Parameters to check accuracy

```{r}
set.seed(333)

newDistM <- rinvgamma(length(bmi90m), shape = 46.2399, scale = 1161.3295)

hist(newDistM)

# combine

datM <- rbind(data.frame(type = "real", bmi = bmi90m),
             data.frame(type = "simulated", bmi = newDistM))

ggplot(datM, aes(x = bmi, colour = type)) + 
  geom_density(size = 2) +
  theme_ipsum() +
  labs(title = "Actual and simulated distribution from HSE 1991 - MALE",
       subtitle = "Inverse Gamma distribution with shape of 46.2 and scale of 1161.3",
       colour = "")

dist91 <- ecdf(bmi90m)
dist0 <- ecdf(newDistM)

# overweight + obese

1 - dist0(25)
1 - dist91(25)

# obese

1 - dist0(30)
1 - dist91(30)
```

## Females

```{r}
bmi90f <- df_low[which(df_low$sex == 2),"bmivalid"] %>% na.omit() %>% as.numeric()

## Step (1) Plot 
descdist( data = bmi90f , discrete = FALSE)
descdist(data = bmi90f, discrete = FALSE, boot=1000)


## Step (2) Fit

normal_ = fitdist(bmi90f, "norm")
weibull_ = fitdist(bmi90f, "weibull")
gamma_ = fitdist(bmi90f, "gamma")
invweibull_ = fitdist(bmi90f, "invweibull")
invgamma_ = fitdist(bmi90f, "invgamma")


plot(normal_)
plot(weibull_)
plot(gamma_)
plot(invweibull_)
plot(invgamma_)

## Step (3) Estimate parameters

print(normal_)
print(weibull_)
print(gamma_)
print(invweibull_)
print(invgamma_)

summary(normal_)
summary(weibull_)
summary(gamma_)
summary(invweibull_)
summary(invgamma_)

gofstat(list(normal_, weibull_, gamma_, invweibull_, invgamma_), 
        fitnames=c("normal", "Weibull", "gamma", "inverseWeibull", "inverseGamma"))

# the best fitting distribution is the inverse gamma with parameters
# shape:  33.76421
# scale: 827.86971
```
The best fitting distribution is the Inverse Gamma with parameters:

* shape = 33.76421
* scale = 827.86971

### Simulate Distribution with Same Parameters to check accuracy

```{r}
set.seed(333)

newDistF <- rinvgamma(length(bmi90f), shape = 33.76421, scale = 827.86971)
 
hist(newDistF)

# combine

datF <- rbind(data.frame(type = "real", bmi = bmi90f),
             data.frame(type = "simulated", bmi = newDistF))

ggplot(datF, aes(x = bmi, colour = type)) + 
  geom_density(size = 2) +
  theme_ipsum() +
  labs(title = "Actual and simulated distribution from HSE 1991 - FEMALE",
       subtitle = "Inverse Gamma distribution with shape of 33.7 and scale of 827.9",
       colour = "")

dist91 <- ecdf(bmi90f)
dist0 <- ecdf(newDistF)

# overweight + obese

1 - dist0(25)
1 - dist91(25)

# obese

1 - dist0(30)
1 - dist91(30)
```
