---
title: "HSE Subgroup Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(plotly)
library(beepr)
library(survey)
library(scales)

# Read flat file Health Survey data

df <- read.csv("C:\\Users\\Elena.Mariani\\Documents\\Projects\\alh_user_personas\\Data\\calorie_deficit_scenarios_extended.csv", sep = ",", fileEncoding="UTF-8-BOM") %>% 
  mutate(Age_group_2 = cut(Age_est, 
                           breaks = c(16, 20, 30, 40, 50, 60, 200), 
                           right = F,
                           labels = c("16-19", "20-29", "30-39", "40-49", "50-59", "60 +"))) %>% 
  mutate(educ = ifelse(topqual3 == 1 ,"Degree or higher", 
                       ifelse(topqual3 %in% c(2,3), "A level or equivalent", 
                              ifelse(topqual3 %in% c(4,5, 7), "GCSE or lower",
                                     ifelse(topqual3 == 6, "Foreign",  NA))))) %>% 
  mutate(work = case_when(Activb2 == 1 ~ "In Education",
                          Activb2 %in% c(2,4) ~ "In Paid Employment/Self Employed",
                          Activb2 %in% c(3,9) ~ "Unpaid Work (including carers)",
                          Activb2 == 5 ~ "Unemployed",
                          Activb2 %in% c(6,7) ~ "Long term illness",
                          Activb2 == 8 ~ "Retired",
                          Activb2 == 95 ~ "Other",
                          TRUE ~ "Missing")) %>% 
  mutate(region = case_when(GOR1 == 1 ~ "North East",
                            GOR1 == 2 ~ "North West",
                            GOR1 == 3 ~ "Yorkshire and the Humber",
                            GOR1 == 4 ~ "East Midlands",
                            GOR1 == 5 ~ "West Midlands",
                            GOR1 == 6 ~ "East of England",
                            GOR1 == 7 ~ "London",
                            GOR1 == 8 ~ "South East",
                            GOR1 == 9 ~ "South West",
                            TRUE ~ "Missing"))

# Declare survey design

hse <- svydesign(id = ~X,
          weights = ~sample_weight,
          data = df)


```

This notebook contains analysis of adults (16 year old and above) from the 2019 Health Survey for England sample. Sample weights have been applied to all analysis. The purpose of this analysis is to gain an initial understanding of the profiles of individuals living with excess weight (overweight or obese) in England. 

# Excess Weight Prevalence

Overall, 35.5% of the adult population is classified as overweight, and 28.2% as obese. 

```{r rate}
# Calculate obesity rate

tab <- svytable(~BMI_class, design = hse)

# Add proportions to table
tab_w <- tab %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

tab_w$BMI_class <- factor(tab_w$BMI_class, levels = c("underweight", "normal", "overweight", "obese"))

# Create a barplot
ggplot(data = tab_w, mapping = aes(x = BMI_class, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,0.7))

# summary stats

svyquantile(~Age_est, hse, quantile=c(0.5), ci=TRUE)
svymean(~Age_est, hse)
svyquantile(~BMI_est, hse, quantile=c(0.5), ci=TRUE)

svytable(~Ethnicity, hse) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~educ, hse) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~work, hse) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~IMD_q, hse) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~region, hse) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))


```

## Gender

There is a statistically significant association between gender and excess weight prevalence, with women over-represented in the obese category and men in the overweight category.

```{r gender chi}
chi_gender <- svychisq(~Sex+BMI_class, hse, statistic="adjWald")
chi_gender
```


```{r gender}
# gender

tab_gender <- svytable(~BMI_class + Sex, design = hse)

# Add proportions to table
tab_w_gender <- tab_gender %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq))) 


# comparison

tab_gender_all <- svytable(~Sex, design = hse)

tab_w_gender_all <- tab_gender_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_gender_final <- rbind(tab_w_gender, tab_w_gender_all) 

tab_w_gender_final$BMI_class <- factor(tab_w_gender_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

 tab_w_gender_final <- tab_w_gender_final %>% 
   group_by(BMI_class) %>% 
   arrange(Sex) %>% 
   mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop)) 

# Create a barplot
ggplot(data = tab_w_gender_final, mapping = aes(x = BMI_class, y = Prop, fill = Sex)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))

```

## Ethnicity

There is a statistically significant association between ethnicity and obesity with white people over-represented in the obese category.

```{r ethnicity chi}
chi_ethnicity <- svychisq(~Ethnicity+BMI_class, hse, statistic="adjWald")
chi_ethnicity
```


```{r ethnicity}
tab_ethn <- svytable(~BMI_class + Ethnicity, design = hse)

# Add proportions to table
tab_w_ethn <- tab_ethn %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq)))

# comparison

tab_ethn_all <- svytable(~Ethnicity, design = hse)

tab_w_ethn_all <- tab_ethn_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_ethn_final <- rbind(tab_w_ethn, tab_w_ethn_all)

tab_w_ethn_final$BMI_class <- factor(tab_w_ethn_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

tab_w_ethn_final$Ethnicity <- factor(tab_w_ethn_final$Ethnicity, levels = c("Asian", "Black", "White", "Mixed", "Other"))

tab_w_ethn_final <- tab_w_ethn_final %>% 
  group_by(BMI_class) %>% 
  arrange(Ethnicity) %>% 
  mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop))

# Create a barplot
ggplot(data = tab_w_ethn_final, mapping = aes(x = BMI_class, y = Prop, fill = Ethnicity)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))
```

## Age group

There is a statistically significant association between age and obesity with people aged 50+ being over-represented in the obese and overweight categories.

```{r age chi}
chi_age <- svychisq(~Age_group_2+BMI_class, hse, statistic="adjWald")
chi_age
```


```{r age}
# Age group

tab_age <- svytable(~BMI_class + Age_group_2, design = hse)

# Add proportions to table
tab_w_age <- tab_age %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq)))

# comparison

tab_age_all <- svytable(~Age_group_2, design = hse)

tab_w_age_all <- tab_age_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_age_final <- rbind(tab_w_age, tab_w_age_all)

tab_w_age_final$BMI_class <- factor(tab_w_age_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

tab_w_age_final <- tab_w_age_final %>% 
  group_by(BMI_class) %>% 
  arrange(Age_group_2) %>% 
  mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop))

# Create a barplot
ggplot(data = tab_w_age_final, mapping = aes(x = BMI_class, y = Prop, fill = Age_group_2)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "", fill = "Age group")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))
```

## Deprivation

There is a statistically significant association between deprivation and obesity with people in the lowest quintiles being over-represented in the obese category.

```{r imd chi}
chi_imd <- svychisq(~IMD_q+BMI_class, hse, statistic="adjWald")
chi_imd
```

```{r IMD}

# Deprivation

tab_imd <- svytable(~BMI_class + IMD_q, design = hse)

# Add proportions to table
tab_w_imd <- tab_imd %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq)))

# comparison

tab_imd_all <- svytable(~IMD_q, design = hse)

tab_w_imd_all <- tab_imd_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_imd_final <- rbind(tab_w_imd, tab_w_imd_all)

tab_w_imd_final$BMI_class <- factor(tab_w_imd_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

tab_w_imd_final <- tab_w_imd_final %>% 
  group_by(BMI_class) %>% 
  arrange(IMD_q) %>% 
  mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop))

# Create a barplot
ggplot(data = tab_w_imd_final, mapping = aes(x = BMI_class, y = Prop, fill = IMD_q)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "", fill = "IMD quintile")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))
```

## Education

```{r education chi}
chi_educ <- svychisq(~educ+BMI_class, hse, statistic="adjWald")
chi_educ
```



```{r education}
# Education

tab_educ <- svytable(~BMI_class + educ, design = hse)

# Add proportions to table
tab_w_educ <- tab_educ %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq)))

# comparison

tab_educ_all <- svytable(~educ, design = hse)

tab_w_educ_all <- tab_educ_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_educ_final <- rbind(tab_w_educ, tab_w_educ_all)

tab_w_educ_final$BMI_class <- factor(tab_w_educ_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

tab_w_educ_final <- tab_w_educ_final %>% 
  group_by(BMI_class) %>% 
  arrange(educ) %>% 
  mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop))

# Create a barplot
ggplot(data = tab_w_educ_final, mapping = aes(x = BMI_class, y = Prop, fill = educ)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "", fill = "Education")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))
```

# Profiling Excess Weight

## Obese

To profile the obese population I divide it in three sections, based on the percentiles of the BMI distribution (below 25%, between 26% and 75% and above 75%).

```{r obese}
obese <- df %>% filter(BMI_class == "obese")

dens <- density(obese$BMI_est)
dat <- data.frame(x=dens$x, y=dens$y)
probs <- c(0, 0.25, 0.5, 0.75, 1)
quantiles <- quantile(obese$BMI_est, prob=probs)
dat$quant <- factor(findInterval(dat$x,quantiles))
ggplot(dat, aes(x,y)) + 
  geom_line() + 
  geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
  scale_x_continuous(breaks=quantiles) + 
  scale_fill_brewer(guide="none") +
  theme_bw() + 
  labs(x = "BMI")


```

### Obese: the lower 25%

```{r obese-low}
obese_low <- obese %>% filter(BMI_est <= quantiles[[2]])

# Declare survey design

obese_low_dsg <- svydesign(id = ~X,
          weights = ~sample_weight,
          data = obese_low)

# summary stats

svyquantile(~Age_est, obese_low_dsg, quantile=c(0.5), ci=TRUE)
svymean(~Age_est, obese_low_dsg)
svyquantile(~BMI_est, obese_low_dsg, quantile=c(0.5), ci=TRUE)

svytable(~Ethnicity, obese_low_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~educ, obese_low_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~work, obese_low_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~IMD_q, obese_low_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~region, obese_low_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))


# Age group

tab_age_low <- svytable(~Age_group_2, design = obese_low_dsg)

# Add proportions to table
tab_age_low_w <- tab_age_low %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_age_low_w, mapping = aes(x = Age_group_2, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Gender

tab_gender_low <- svytable(~Sex, design = obese_low_dsg)

# Add proportions to table
tab_gender_low_w <- tab_gender_low %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_gender_low_w, mapping = aes(x = Sex, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Education

tab_educ_low <- svytable(~educ, design = obese_low_dsg)

# Add proportions to table
tab_educ_low_w <- tab_educ_low %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_educ_low_w, mapping = aes(x = educ, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Ethnicity

tab_ethn_low <- svytable(~Ethnicity, design = obese_low_dsg)

# Add proportions to table
tab_ethn_low_w <- tab_ethn_low %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_ethn_low_w, mapping = aes(x = Ethnicity, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Deprivation

tab_imd_low <- svytable(~IMD_q, design = obese_low_dsg)

# Add proportions to table
tab_imd_low_w <- tab_imd_low %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_imd_low_w, mapping = aes(x = IMD_q, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Work

tab_work_low <- svytable(~work, design = obese_low_dsg)

# Add proportions to table
tab_work_low_w <- tab_work_low %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_work_low_w, mapping = aes(x = work, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

### Obese: the mid 50%

```{r obese-med}
obese_med <- obese %>% filter(BMI_est > quantiles[[2]] & BMI_est <= quantiles[[4]])

# Declare survey design

obese_med_dsg <- svydesign(id = ~X,
          weights = ~sample_weight,
          data = obese_med)

# summary stats

svyquantile(~Age_est, obese_med_dsg, quantile=c(0.5), ci=TRUE)
svymean(~Age_est, obese_med_dsg)

svyquantile(~BMI_est, obese_med_dsg, quantile=c(0.5), ci=TRUE)

svytable(~Ethnicity, obese_med_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~educ, obese_med_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~work, obese_med_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~IMD_q, obese_med_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~region, obese_med_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))

# Age group

tab_age_med <- svytable(~Age_group_2, design = obese_med_dsg)

# Add proportions to table
tab_age_med_w <- tab_age_med %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_age_med_w, mapping = aes(x = Age_group_2, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Gender

tab_gender_med <- svytable(~Sex, design = obese_med_dsg)

# Add proportions to table
tab_gender_med_w <- tab_gender_med %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_gender_med_w, mapping = aes(x = Sex, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Education

tab_educ_med <- svytable(~educ, design = obese_med_dsg)

# Add proportions to table
tab_educ_med_w <- tab_educ_med %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_educ_med_w, mapping = aes(x = educ, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Ethnicity

tab_ethn_med <- svytable(~Ethnicity, design = obese_med_dsg)

# Add proportions to table
tab_ethn_med_w <- tab_ethn_med %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_ethn_med_w, mapping = aes(x = Ethnicity, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Deprivation

tab_imd_med <- svytable(~IMD_q, design = obese_med_dsg)

# Add proportions to table
tab_imd_med_w <- tab_imd_med %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_imd_med_w, mapping = aes(x = IMD_q, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Work

tab_work_med <- svytable(~work, design = obese_med_dsg)

# Add proportions to table
tab_work_med_w <- tab_work_med %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_work_med_w, mapping = aes(x = work, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

### Obese: the top 25%

```{r obese-high}
obese_high <- obese %>% filter(BMI_est > quantiles[[4]])

# Declare survey design

obese_high_dsg <- svydesign(id = ~X,
          weights = ~sample_weight,
          data = obese_high)

# summary stats

svyquantile(~Age_est, obese_high_dsg, quantile=c(0.5), ci=TRUE)
svymean(~Age_est, obese_high_dsg)
svyquantile(~BMI_est, obese_high_dsg, quantile=c(0.5), ci=TRUE)

svytable(~Ethnicity, obese_high_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~educ, obese_high_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~work, obese_high_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~IMD_q, obese_high_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))
svytable(~region, obese_high_dsg) %>% as.data.frame() %>% mutate(Prop = (Freq/sum(Freq)))


# Age group

tab_age_high <- svytable(~Age_group_2, design = obese_high_dsg)

# Add proportions to table
tab_age_high_w <- tab_age_high %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_age_high_w, mapping = aes(x = Age_group_2, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Gender

tab_gender_high <- svytable(~Sex, design = obese_high_dsg)

# Add proportions to table
tab_gender_high_w <- tab_gender_high %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_gender_high_w, mapping = aes(x = Sex, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Education

tab_educ_high <- svytable(~educ, design = obese_high_dsg)

# Add proportions to table
tab_educ_high_w <- tab_educ_high %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_educ_high_w, mapping = aes(x = educ, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Ethnicity

tab_ethn_high <- svytable(~Ethnicity, design = obese_high_dsg)

# Add proportions to table
tab_ethn_high_w <- tab_ethn_high %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_ethn_high_w, mapping = aes(x = Ethnicity, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Deprivation

tab_imd_high <- svytable(~IMD_q, design = obese_high_dsg)

# Add proportions to table
tab_imd_high_w <- tab_imd_high %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_imd_high_w, mapping = aes(x = IMD_q, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 

# Work

tab_work_high <- svytable(~work, design = obese_high_dsg)

# Add proportions to table
tab_work_high_w <- tab_work_high %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

ggplot(data = tab_work_high_w, mapping = aes(x = work, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```