---
title: "HSE Subgroup Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(plotly)
library(beepr)
library(survey)
library(scales)

# Read flat file Health Survey data

df <- read.csv("C:\\Users\\Elena.Mariani\\Documents\\Projects\\ahl_weight_loss_modelling\\Data\\calorie_deficit_scenarios_w_imd.csv", sep = ",", fileEncoding="UTF-8-BOM")

# Create grouped age groups

df <- df %>% 
  mutate(Age_group_2 = cut(Age_est, 
                           breaks = c(16, 20, 30, 40, 50, 60, 200), 
                           right = F,
                           labels = c("16-19", "20-29", "30-39", "40-49", "50-59", "60 +")))

# Declare survey design

hse <- svydesign(id = ~X,
          weights = ~sample_weight,
          data = df)


```

This notebook contains analysis of adults (16 year old and above) from the 2019 Health Survey for England sample. Sample weights have been applied to all analysis. The purpose of this analysis is to gain an initial understanding of the profiles of individuals living with excess weight (overweight or obese) in England. 

## Excess Weight Prevalence

Overall, 35.5% of the adult population is classified as overweight, and 28.2% as obese. 

```{r rate}
# Calculate obesity rate

tab <- svytable(~BMI_class, design = hse)

# Add proportions to table
tab_w <- tab %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq)))

tab_w$BMI_class <- factor(tab_w$BMI_class, levels = c("underweight", "normal", "overweight", "obese"))

# Create a barplot
ggplot(data = tab_w, mapping = aes(x = BMI_class, y = Prop)) + 
  geom_col(fill = "blue") +
  geom_text(aes(label = label_percent()(Prop)), vjust = -0.3, size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,0.7))

```

## Gender



```{r gender}
# gender

tab_gender <- svytable(~BMI_class + Sex, design = hse)

# Add proportions to table
tab_w_gender <- tab_gender %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(label_y = cumsum(Prop) - 0.5 * Prop)


# comparison

tab_gender_all <- svytable(~Sex, design = hse)

tab_w_gender_all <- tab_gender_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(label_y = cumsum(Prop) - 0.5 * Prop) %>% 
  mutate(BMI_class = "All")

tab_w_gender_final <- rbind(tab_w_gender, tab_w_gender_all)

tab_w_gender_final$BMI_class <- factor(tab_w_gender_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))


# Create a barplot
ggplot(data = tab_w_gender_final, mapping = aes(x = BMI_class, y = Prop, fill = Sex)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))

```

## Ethnicity

```{r ethnicity}
tab_ethn <- svytable(~BMI_class + Ethnicity, design = hse)

# Add proportions to table
tab_w_ethn <- tab_ethn %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq)))

# comparison

tab_ethn_all <- svytable(~Ethnicity, design = hse)

tab_w_ethn_all <- tab_ethn_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_ethn_final <- rbind(tab_w_ethn, tab_w_ethn_all)

tab_w_ethn_final$BMI_class <- factor(tab_w_ethn_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

tab_w_ethn_final$Ethnicity <- factor(tab_w_ethn_final$Ethnicity, levels = c("Asian", "Black", "White", "Mixed", "Other"))

tab_w_ethn_final <- tab_w_ethn_final %>% 
  group_by(BMI_class) %>% 
  arrange(Ethnicity) %>% 
  mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop))

# Create a barplot
ggplot(data = tab_w_ethn_final, mapping = aes(x = BMI_class, y = Prop, fill = Ethnicity)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))
```

## Age group

```{r age}
# Age group

tab_age <- svytable(~BMI_class + Age_group_2, design = hse)

# Add proportions to table
tab_w_age <- tab_age %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq)))

# comparison

tab_age_all <- svytable(~Age_group_2, design = hse)

tab_w_age_all <- tab_age_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_age_final <- rbind(tab_w_age, tab_w_age_all)

tab_w_age_final$BMI_class <- factor(tab_w_age_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

tab_w_age_final <- tab_w_age_final %>% 
  group_by(BMI_class) %>% 
  arrange(Age_group_2) %>% 
  mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop))

# Create a barplot
ggplot(data = tab_w_age_final, mapping = aes(x = BMI_class, y = Prop, fill = Age_group_2)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "", fill = "Age group")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))
```

## Deprivation

```{r IMD}

# Deprivation

tab_imd <- svytable(~BMI_class + IMD_q, design = hse)

# Add proportions to table
tab_w_imd <- tab_imd %>%
  as.data.frame() %>%
  group_by(BMI_class) %>% 
  mutate(Prop = (Freq/sum(Freq)))

# comparison

tab_imd_all <- svytable(~IMD_q, design = hse)

tab_w_imd_all <- tab_imd_all %>%
  as.data.frame() %>%
  mutate(Prop = (Freq/sum(Freq))) %>% 
  mutate(BMI_class = "All")

tab_w_imd_final <- rbind(tab_w_imd, tab_w_imd_all)

tab_w_imd_final$BMI_class <- factor(tab_w_imd_final$BMI_class, levels = c("underweight", "normal", "overweight", "obese", "All"))

tab_w_imd_final <- tab_w_imd_final %>% 
  group_by(BMI_class) %>% 
  arrange(IMD_q) %>% 
  mutate(label_y = 1 - (cumsum(Prop) - 0.5 * Prop))

# Create a barplot
ggplot(data = tab_w_imd_final, mapping = aes(x = BMI_class, y = Prop, fill = IMD_q)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = label_y, label = label_percent(1)(Prop)), size = 3.5) +
  theme_bw() +
  labs(x = "", y = "", fill = "IMD quintile")+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0,1))
```